---
title: "Fraud"
author: "Christine Iyer"
date: "October 2, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We are delighted to have you continue on in our interview process!
Please complete the scenario below. The set of data needed to review is attached separately as an excel
document. Feel free to manipulate the document. You will be presenting your solution and findings
during your onsite interview with the management team.

Operational Scenario:
*See Excel Document Attached

We have 3 locations staffed with manual fraud reviewers: Atlantic City, Montreal, and Ibiza. Fraud
reviewers in this position will evaluate orders for fraudulent activity and decide to cancel or pass the
order. We have 13 total reviewers that we can allocate to any location. Each reviewer can look at 100
orders per hour and work 8 hours total per day.

* Atlantic City is staffed from 8a-6p EST

* Montreal is staffed from 10a-9p EST

* Ibiza is staffed from 2a-10a EST

Using the data in the attached spreadsheet please analyze and recommend your staffing
recommendations for all 3 locations assuming that this data will remain constant year round. The
spreadsheet contains one month of order data with order times and dates. In addition to a staffing
recommendation please highlight any other trends that you see in our fraud data. Would you have any
further questions on the ask? What would your next steps be?
Please be ready to make your recommendation and highlight any trends that you find in a short 5-
minute presentation using your preferred method to present (Power Point, Excel, etc...).



```{r}
library(knitr)
library(dplyr)
library(ggplot2)
```

```{r}
fraud <- read.csv("test_frauddata.csv", header = T, stringsAsFactors = F)
fraud$OrderDate <- as.Date(fraud$OrderDate, format = "%m/%d/%Y")

fraud <- fraud %>% rename(Fraudulent = OrderIsFraudulent..1.yes..0.No., Revenue = OrderRevenue,State = OrderState )
kable(head(fraud))
```

```{r}
str(fraud)

ggplot(fraud, aes(x = OrderDate))
range(fraud$OrderDate)
```

